### 2023-09-16 my_paper/tables/tab35-asianiat_regression_tab_byparent_type.tex
edit tables and figures

\caption{Subjective Hispanic identity and GSS Bias Among Second Generation Hispanic Immigrants: By Parental Type (State)\label{regtab-byparent-04}}

@@

\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{HH} & \multicolumn{1}{c}{HW} & \multicolumn{1}{c}{WH} \\

@@

Bias & \num{0.03} & \num{0.01} & \num{0.12}** & \num{-0.10} & \num{0.02} & \num{-0.01} & \num{0.00} & \num{-0.02} & \num{0.04} & \num{0.01} & \num{0.13}** & \num{-0.10} & \num{0.02} & \num{-0.01} & \num{0.01} & \num{-0.03}\\
 & (\num{0.03}) & (\num{0.03}) & (\num{0.10}) & (\num{0.12}) & (\num{0.03}) & (\num{0.03}) & (\num{0.10}) & (\num{0.20}) & (\num{0.03}) & (\num{0.03}) & (\num{0.10}) & (\num{0.12}) & (\num{0.03}) & (\num{0.03}) & (\num{0.09}) & (\num{0.20})\\
Female & \num{0.00} & \num{0.00} & \num{-0.01}** & \num{0.01}** & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.02}** & \num{0.00} & \num{0.00} & \num{-0.01}** & \num{0.01}** & \num{0.00} & \num{0.00} & \num{0.00} & \num{0.02}**\\
 & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.01}) & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.02}) & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.01}) & (\num{0.00}) & (\num{0.00}) & (\num{0.01}) & (\num{0.02})\\
College Graduate: Mother & \num{-0.08}*** & \num{-0.04}*** & \num{-0.11}*** & \num{-0.11}*** & \num{-0.08}*** & \num{-0.05}*** & \num{-0.09}*** & \num{-0.10}*** & \num{-0.08}*** & \num{-0.04}*** & \num{-0.11}*** & \num{-0.11}*** & \num{-0.07}*** & \num{-0.05}*** & \num{-0.08}*** & \num{-0.09}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.01}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.01}) & (\num{0.02}) & (\num{0.02}) & (\num{0.02})\\
College Graduate: Father & \num{-0.10}*** & \num{-0.04}*** & \num{-0.16}*** & \num{-0.15}*** & \num{-0.10}*** & \num{-0.04}*** & \num{-0.17}*** & \num{-0.13}*** & \num{-0.10}*** & \num{-0.04}*** & \num{-0.16}*** & \num{-0.16}*** & \num{-0.10}*** & \num{-0.04}*** & \num{-0.16}*** & \num{-0.12}***\\
 & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.02}) & (\num{0.01}) & (\num{0.01}) & (\num{0.02}) & (\num{0.01}) & (\num{0.01}) & (\num{0.01}) & (\num{0.03}) & (\num{0.02})\\
Log Total Family Income &  &  &  &  &  &  &  &  &  &  &  &  & \num{0.00}*** & \num{0.00}* & \num{-0.01}*** & \num{-0.02}***\\
 &  &  &  &  &  &  &  &  &  &  &  &  & (\num{0.00}) & (\num{0.00}) & (\num{0.00}) & (\num{0.00})\\

@@

Mean & \num{0.92} & \num{0.96} & \num{0.83} & \num{0.77} & \num{0.93} & \num{0.97} & \num{0.85} & \num{0.8} & \num{0.92} & \num{0.96} & \num{0.82} & \num{0.77} & \num{0.93} & \num{0.97} & \num{0.85} & \num{0.8}\\
N & \num{293112} & \num{209966} & \num{47324} & \num{35822} & \num{41973} & \num{30332} & \num{6675} & \num{4966} & \num{251139} & \num{179634} & \num{40649} & \num{30856} & \num{41973} & \num{30332} & \num{6675} & \num{4966}\\

@@

\multicolumn{17}{l}{\rule{0pt}{1em}** p $<$ 0.29, * p $<$ 0.1, *** p $<$ 0.01}\\

>>>>

\caption{Subjective Asian Identity and Implicit Bias Among Second Generation Asian Immigrants: By Parental Type (State)\label{regtab-byparent-06}}

@@

\multicolumn{1}{c}{Parents Type} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{AA} & \multicolumn{1}{c}{AW} & \multicolumn{1}{c}{WA} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{AA} & \multicolumn{1}{c}{AW} & \multicolumn{1}{c}{WA} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{AA} & \multicolumn{1}{c}{AW} & \multicolumn{1}{c}{WA} & \multicolumn{1}{c}{All} & \multicolumn{1}{c}{AA} & \multicolumn{1}{c}{AW} & \multicolumn{1}{c}{WA} \\

@@

Implicit Bias & -0.54*** & -0.13* & -1.21*** & -0.99*** & -0.57*** & -0.14* & -1.31*** & -0.93*** & -0.54*** & -0.12* & -1.20*** & -0.99*** & -0.58*** & -0.14* & -1.32*** & -0.94***\\
 & (0.08) & (0.06) & (0.21) & (0.17) & (0.07) & (0.08) & (0.27) & (0.18) & (0.08) & (0.06) & (0.22) & (0.18) & (0.07) & (0.08) & (0.27) & (0.18)\\
Female & 0.00 & 0.00 & -0.01 & 0.02 & 0.00 & 0.00 & 0.00 & 0.03** & 0.00 & 0.00 & -0.01 & 0.01 & 0.00 & 0.00 & 0.00 & 0.03**\\
 & (0.00) & (0.00) & (0.01) & (0.01) & (0.01) & (0.00) & (0.02) & (0.02) & (0.00) & (0.00) & (0.01) & (0.01) & (0.01) & (0.00) & (0.02) & (0.02)\\
College Graduate: Mother & 0.00 & -0.01 & 0.06* & 0.01 & -0.01 & -0.01* & 0.07* & -0.01 & 0.00 & -0.01 & 0.06* & 0.01 & 0.00 & -0.01* & 0.07* & -0.01\\
 & (0.01) & (0.01) & (0.03) & (0.02) & (0.01) & (0.01) & (0.04) & (0.03) & (0.01) & (0.01) & (0.03) & (0.02) & (0.01) & (0.01) & (0.04) & (0.03)\\
College Graduate: Father & 0.01 & 0.01* & -0.03 & 0.01 & 0.01 & 0.01** & -0.05 & 0.02 & 0.01 & 0.01* & -0.03 & 0.01 & 0.01 & 0.01** & -0.05 & 0.02\\
 & (0.01) & (0.01) & (0.03) & (0.03) & (0.01) & (0.01) & (0.04) & (0.03) & (0.01) & (0.01) & (0.03) & (0.03) & (0.01) & (0.01) & (0.05) & (0.03)\\
Log Total Family Income &  &  &  &  &  &  &  &  &  &  &  &  & 0.00 & 0.00 & 0.00 & -0.01\\
 &  &  &  &  &  &  &  &  &  &  &  &  & (0.00) & (0.00) & (0.02) & (0.01)\\

@@

Mean & 0.72 & 0.96 & 0.38 & 0.32 & 0.71 & 0.96 & 0.37 & 0.31 & 0.72 & 0.96 & 0.38 & 0.32 & 0.71 & 0.96 & 0.37 & 0.31\\
N & 167709 & 103697 & 19982 & 44030 & 21584 & 13242 & 2706 & 5636 & 146125 & 90455 & 17276 & 38394 & 21584 & 13242 & 2706 & 5636\\

@@

\multicolumn{17}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\

### 2023-09-16 output/tables/tab04-regression_tab_bygen_skin.tex
edit tables and figures

\caption{Relationship Between Bias and Self-Reported Hispanic Identity: By Generation \label{regtab-bygen-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ All Gens \\ $H_{ist}$} & \specialcell{(2) \\  First Gen \\ $H^1_{ist}$} & \specialcell{(3) \\  Second Gen \\ $H^2_{ist}$} & \specialcell{(4) \\  Third Gen \\ $H^3_{ist}$}\\
\midrule
Bias & -0.10** & -0.07* & -0.13** & -0.02\\
 & (0.04) & (0.04) & (0.05) & (0.07)\\
Female & 0.00 & 0.00 & 0.00 & 0.00\\
 & (0.00) & (0.00) & (0.00) & (0.00)\\
College Graduate: Mother & -0.05*** & -0.03*** & -0.06*** & -0.07***\\
 & (0.01) & (0.01) & (0.01) & \vphantom{1} (0.01)\\
College Graduate: Father & -0.06*** & -0.06*** & -0.08*** & -0.08***\\
 & (0.01) & (0.01) & (0.01) & (0.01)\\
\midrule
Observations & 844,481 & 85,390 & 560,100 & 198,991\\
Mean & 0.91 & 0.96 & 0.94 & 0.82\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      generation with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Hispanics in a state, and parental education.
                      I also added parents' (HH, HW, and WH) and grandparents' (HHHH, HHHW, HHWH, etc.) type dummy variables to the regression
                      on second and third generation immigrants, where H is objectively Hispanic (born in a Spanish-Speaking Country) and W is objectively White (native-born). 
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Hispanic immigrant children that were born in a 
                      Spanish-speaking county. Native-born second-generation Hispanic 
                      immigrant children with at least one parent born in a Spanish-speaking 
                      country. Finally, native-born third-generation Hispanic immigrant children 
                      with native-born parents and at least one grandparent born in a Spanish-
                      speaking country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

>>>>

\caption{Relationship Between Bias and Self-Reported Asian Identity: By Generation \label{regtab-bygen-01}}
\centering
\resizebox{\linewidth}{!}{
\begin{threeparttable}
\begin{tabular}[t]{lcccc}
\toprule
  & \specialcell{(1) \\ All Gens \\ $H_{ist}$} & \specialcell{(2) \\  First Gen \\ $H^1_{ist}$} & \specialcell{(3) \\  Second Gen \\ $H^2_{ist}$} & \specialcell{(4) \\  Third Gen \\ $H^3_{ist}$}\\
\midrule
Bias & -0.26*** & -0.12 & -0.45*** & -0.43***\\
 & (0.06) & (0.08) & (0.09) & (0.11)\\
Female & 0.00 & -0.02*** & 0.00 & 0.00\\
 & (0.00) & (0.01) & (0.00) & (0.01)\\
College Graduate: Mother & 0.00 & -0.01 & 0.01 & 0.01\\
 & (0.01) & (0.01) & (0.01) & (0.01)\\
College Graduate: Father & 0.01* & 0.02** & 0.01 & -0.01\\
 & (0.00) & (0.01) & (0.01) & (0.01)\\
\midrule
Observations & 268,677 & 31,586 & 167,709 & 69,382\\
Mean & 0.65 & 0.47 & 0.23 & 0.66\\
Year $\times$ Region FE & X & X & X & X\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{Each column is an estimation of a heterogeneous effect of regression (\ref{eq:identity_reg_bias}) by 
                      generation with region × year fixed effects. 
                      I include controls for sex, quartic age, fraction of Asians in a state, and parental education.
                      I also added parents' (HH, HW, and WH) and grandparents' (HHHH, HHHW, HHWH, etc.) type dummy variables to the regression
                      on second and third generation immigrants, where H is objectively Asian (born in a Asian country) and W is objectively White (native-born). 
                      Standard errors are clustered on the state level.}
\item[2] \footnotesize{The samples include children ages 17 and below who live in intact families. 
                      First-generation Asian immigrant children that were born in a 
                      Asian country. Native-born second-generation Asian 
                      immigrant children with at least one parent born in a Asian 
                      country. Finally, native-born third-generation Asian immigrant children 
                      with native-born parents and at least one grandparent born in a Asian country.}
\item[3] \footnotesize{Data source is the 2004-2021 Current Population Survey.}
\end{tablenotes}
\end{threeparttable}}
\end{table}

### 2023-09-16 output/tables/tab41a-marriage.tex
edit tables and figures

\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Hispanic Men} & \multicolumn{1}{c}{Hispanic Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & 0.05*** & 0.06*** & 0.07***\\
 & (0.01) & (0.01) & (0.01)\\
College Graduate: Wife & 0.05*** & 0.04*** & 0.04***\\
 & (0.00) & (0.00) & \vphantom{1} (0.00)\\
College Graduate: Husband & 0.08*** & 0.04*** & 0.06***\\
 & (0.00) & (0.00) & (0.00)\\
\midrule
Observations & 477,672 & 433,232 & 434,297\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}

>>>>

\caption{Relationship Between Bias and Interethnic Marriages \label{regtab-logit-02}}
\centering
\begin{threeparttable}
\begin{tabular}[t]{lccc}
\toprule
\multicolumn{2}{c}{ } & \multicolumn{1}{c}{Asian Men} & \multicolumn{1}{c}{Asian Women} \\
\cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4}
  & \specialcell{(1) \\ Interethnic} & \specialcell{(2) \\ Interethnic} & \specialcell{(3) \\ Interethnic}\\
\midrule
Bias & 0.11*** & -0.20*** & -0.03\\
 & (0.03) & (0.03) & (0.03)\\
College Graduate: Wife & 0.03*** & 0.03*** & 0.03***\\
 & (0.00) & (0.00) & \vphantom{1} (0.00)\\
College Graduate: Husband & 0.01* & 0.00 & 0.00\\
 & (0.00) & (0.00) & (0.00)\\
\midrule
Observations & 146,125 & 108,152 & 125,085\\
Year $\times$ Region FE & X & X & X\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ 0.1, ** p $<$ 0.05, *** p $<$ 0.01}\\
\end{tabular}
\begin{tablenotes}
\small
\item[1] \footnotesize{This is the result to estimating (\ref{eq:inter-interethnic}) as a
                      linear probability model.}
\item[2] \footnotesize{I include controls for partners' sex, age, education, 
                      and years since immigrating to the United States.
                      Standard errors are clustered on the household level.}
\item[3] \footnotesize{Data source is the 2004-2020 Current Population Survey Data.}
\end{tablenotes}
\end{threeparttable}
\end{table}
